
Red Snapper Video Index Using Delta GLM
========


```{r prelim,echo=FALSE,message=FALSE, warning=FALSE,error=FALSE}
rm(list=ls(all=TRUE)) 
graphics.off()
windows(record=T)
setwd ("\\\\CCFHR-S-1534090\\popdyn1\\SEDAR\\SEDAR 41\\SEFISIndices\\S41RGIT")
library(MASS)
library(doBy)
library(statmod)
library(Hmisc)
library(pscl)
library(rjags)



```

```{r ReadData, echo=FALSE,message=FALSE, warning=FALSE,error=FALSE}
 # Read in Red Snapper Data
rs=read.csv("\\\\CCFHR-S-1534090\\popdyn1\\SEDAR\\SEDAR 41\\SEFISIndices\\ConfData\\RedSnapGLMData.csv")#;head(rs)
````

```{r ConditionData, echo=FALSE,message=FALSE, warning=FALSE}
# Full data subsetting: 
rs <- rs[rs$Station_Type!="Recon",]                # remove recon stations
rs <- rs[rs$A.Video.Readable == "Yes",]         # remove invalid videos
rs <- subset(rs, rs$Start_Depth > 0)                  # remove NA in depth
rs <- subset(rs, rs$Start_Depth < 100)              # remove < 100 m deep
rs <- subset(rs, rs$LastOfTemp > 0)                 # remove blank water temps
rs <- subset(rs, rs$Turbidity != "Unknown")    # remove unknown turbidity values
rs <- subset(rs, rs$No.Readable.Frames ==41)    # remove zero readable frames

#Eliminate unnecessary columns
dat=subset(rs,select=c(MC_Lutjanus.campechanus,No.Readable.Frames,Year,Turbidity,Current_Direction,Current_Magnitude,Substrate_Cat,Relief,Size,Biotic_Density_Cat,Biotic_Type,Biotic_Height,Start_Depth,Julian,Start_Latitude,LastOfTemp,TOD))
orgnames=names(dat)

sumcount=round(dat$MC_Lutjanus.campechanus*rs$No.Readable.Frames,0)
dat$MC_Lutjanus.campechanus=sumcount

#rename to short names
names(dat)=c('fishseen','frames','y','wc','cd','cm','sc','sr','ss','bd','bt','bh','d','t','lat','temp','tod')#;head(dat)

#replace NA in the cpue with 0
dat$fishseen[is.na(dat$fishseen)]=0

#rescale frames
#dat$frames=dat$frames/41
#dat$frames=log(dat$frames)
#now categorize the continuous variables
#depth
hist(dat$d,breaks=seq(10,110,by=5))
summary(dat$d)
#temp=cut(dat$d,breaks=c(14,25,41,52,115),labels=FALSE)#;temp;table(temp)
#temp=cut(dat$d,2,breaks=c(0,as.numeric(summary(dat$d))[-c(1,4)]),labels=FALSE);temp;table(temp)
temp=cut(dat$d,2,breaks=quantile(dat$d),labels=FALSE)#;temp;table(temp)
dat$d=temp

#latitude
hist(dat$lat,breaks=seq(27,36,by=0.25))
summary(dat$lat)
#temp=cut(dat$lat,breaks=c(27,29.75,31.25,32.75,34,35.25),labels=FALSE)#;temp;table(temp)
#temp=cut(dat$lat,2,breaks=c(0,as.numeric(summary(dat$lat))[-c(1,4)]),labels=FALSE);temp;table(temp)
temp=cut(dat$lat,2,breaks=quantile(dat$lat),labels=FALSE)#;temp;table(temp)
dat$lat=temp

#day of year (t)
hist(dat$t,breaks=seq(110,305,by=5))
summary(dat$t)
#temp=cut(dat$t,breaks=c(##,##,##,##,##,##),labels=FALSE)#;temp;table(temp)
#temp=cut(dat$t,2,breaks=c(0,as.numeric(summary(dat$t))[-c(1,4)]),labels=FALSE);temp;table(temp)
temp=cut(dat$t,2,breaks=quantile(dat$t),labels=FALSE)#;temp;table(temp)
dat$t=temp

#water temperature (temp)
hist(dat$temp,breaks=seq(12.25,29.25,by=0.25))
summary(dat$temp)
#temp=cut(dat$t,breaks=c(##,##,##,##,##,##),labels=FALSE)#;temp;table(temp)
#temp=cut(dat$temp,2,breaks=c(0,as.numeric(summary(dat$temp))[-c(1,4)]),labels=FALSE);temp;table(temp)
temp=cut(dat$temp,2,breaks=quantile(dat$temp),labels=FALSE)#;temp;table(temp)
dat$temp=temp

#time of day (tod)
hist(dat$tod,breaks=seq(0.4,0.95,by=0.025))
summary(dat$tod)
#temp=cut(dat$tod,breaks=c(##,##,##,##,##,##),labels=FALSE)#;temp;table(temp)
#temp=cut(dat$tod,2,breaks=c(0,as.numeric(summary(dat$tod))[-c(1,4)]),labels=FALSE);temp;table(temp)
temp=cut(dat$tod,2,breaks=quantile(dat$tod),labels=FALSE)#;temp;table(temp)
dat$tod=temp

#Factorize variables
dat$y=factor(dat$y)
dat$d=factor(dat$d)
dat$lat=factor(dat$lat)
dat$t=factor(dat$t)
dat$temp=factor(dat$temp)
dat$tod=factor(dat$tod)

#get rid of unused factors for dat$wc
dat$wc=factor(dat$wc)

plot.design(fishseen~y + wc + cd + cm ,data=dat)
plot.design(fishseen~y + wc + sc + sr + ss ,data=dat)
plot.design(fishseen~y + wc + bd + bt + bh ,data=dat)
plot.design(fishseen~y + wc +  d + t + lat + temp + tod,data=dat)
plot.design(fishseen~y + wc + cd + cm + sc + sr + ss + bd + bt + bh + d + t + lat + temp + tod,data=dat)

```

**So this bit allows variable selection of each of the model types**
```{r jags}


modelFilename = "BayesZip"
  cat("
model {
#First set up the prior Weight Parameters

for(i in 1:wgts){
      w[i] ~ dbern(.5)
      }


#Priors parameters
 
# For the non zero infl part
  
    for(i in 1:1){
      alph[i] ~ dt(0,pow(1.566267,-2),7.63179)#dnorm(0,.1)
    }

# For the non zero infl part
    for(i in 1:28){
      bet[i] ~ dt(0,pow(1.566267,-2),7.63179)
    }


#model
   for (i in 1:samp){
    


     log.ypred[i] <- bet[1]+
w[1]*(bet[2]*y2011[i]+bet[3]*y2012[i])+
w[2]*(bet[4]*wc.1[i]+bet[5]*wc.2[i])+
w[3]*(bet[6]*cd.s[i]+bet[7]*cd.t[i]+bet[8]*cd.u[i])+
w[4]*(bet[9]*sc.l[i]+bet[10]*sc.m[i]+bet[11]*sc.n[i]+bet[12]*sc.u[i])+
w[5]*(bet[13]*bd.l[i]+bet[14]*bd.m[i]+bet[15]*bd.n[i]+bet[16]*bd.u[i])+
w[6]*(bet[17]*d.2[i]+bet[18]*d.3[i]+bet[19]*d.4[i])+
w[7]*(bet[20]*t.2[i]+bet[21]*t.3[i]+bet[22]*t.4[i])+
w[8]*(bet[23]*lat.2[i]+bet[24]*lat.3[i]+bet[25]*lat.4[i])+
w[9]*(bet[26]*temp.2[i]+bet[27]*temp.3[i]+bet[28]*temp.4[i])



logit.psi[i] <- alph[1]
    
#Use This bit for the psi-lambda link
#logit.psi[i] <- alph[1]+w[10]*alph[2]*log.ypred[i]


###Use this bit to have the global model for detection
#w[10]*(alph[2]*y2011[i]+alph[3]*y2012[i])+
#w[11]*(alph[4]*wc.1[i]+alph[5]*wc.2[i])+
#w[12]*(alph[6]*cd.s[i]+alph[7]*cd.t[i]+alph[8]*cd.u[i])+
#w[13]*(alph[9]*sc.l[i]+alph[10]*sc.m[i]+alph[11]*sc.n[i]+alph[12]*sc.u[i])+
#w[14]*(alph[13]*bd.l[i]+alph[14]*bd.m[i]+alph[15]*bd.n[i]+alph[16]*bd.u[i])+
#w[15]*(alph[17]*d.2[i]+alph[18]*d.3[i]+alph[19]*d.4[i])+
#w[16]*(alph[20]*t.2[i]+alph[21]*t.3[i]+alph[22]*t.4[i])+
#w[17]*(alph[23]*lat.2[i]+alph[24]*lat.3[i]+alph[25]*lat.4[i])+
#w[18]*(alph[26]*temp.2[i]+alph[27]*temp.3[i]+alph[28]*temp.4[i])




   psi[i]<-1/(1+exp(-logit.psi[i]))
   ypred[i]<-exp(log.ypred[i])
   z[i] ~ dbern(psi[i])
   lambda[i] <- z[i]*ypred[i]
   fishseen[i] ~ dpois(lambda[i])
           }
   }
             
", fill=TRUE, file=modelFilename)


dat$d=sample(c("1","2","3","4"),dim(dat)[1],replace=T)
jags.data = list(fishseen=dat$fishseen,y2011=as.numeric(dat$y=='2011'), y2012=as.numeric(dat$y=='2012'),
                 wc.1=as.numeric(dat$wc==1),wc.2=as.numeric(dat$wc==2),
                 cd.s=as.numeric(dat$cd=="Sideways"),cd.t=as.numeric(dat$cd=="Towards"),cd.u=as.numeric(dat$cd=="Unknown"),
                 #cm.s=as.numeric(dat$cm=="Strong"),cm.u=as.numeric(dat$cm=="Unknown"),
                 sc.l=as.numeric(dat$sc=="Low"),sc.m=as.numeric(dat$sc=="Moderate"),sc.n=as.numeric(dat$sc=="None"),sc.u=as.numeric(dat$sc=="Unknown"),
                 #sr.l=as.numeric(dat$sr=="Low"),sr.m=as.numeric(dat$sr=="Moderate"),sr.u=as.numeric(dat$sr=="Unknown"),
                 #ss.cont=as.numeric(dat$ss=="Continuous"),ss.na=as.numeric(dat$ss=="N/A"),ss.u=as.numeric(dat$ss=="Unknown"),
                 bd.l=as.numeric(dat$bd=="Low"),bd.m=as.numeric(dat$bd=="Moderate"),bd.n=as.numeric(dat$bd=="None"),bd.u=as.numeric(dat$bd=="Unknown"),
                 #bt.na=as.numeric(dat$bt=="N/A"), bt.o=as.numeric(dat$bt=="Other"), bt.u=as.numeric(dat$bt=="Unknown"),
                 #bh.l=as.numeric(dat$bh=="Low"), bh.na=as.numeric(dat$bh=="N/A"), bh.u=as.numeric(dat$bh=="Unknown"),
                 d.2=as.numeric(dat$d=="2"),d.3=as.numeric(dat$d=="3"),d.4=as.numeric(dat$d=="4"),
                 t.2=as.numeric(dat$t=="2"),t.3=as.numeric(dat$t=="3"),t.4=as.numeric(dat$t=="4"),
                 lat.2=as.numeric(dat$lat=="2"),lat.3=as.numeric(dat$lat=="3"),lat.4=as.numeric(dat$lat=="4"),
                 temp.2=as.numeric(dat$temp=="2"),temp.3=as.numeric(dat$temp=="3"),temp.4=as.numeric(dat$temp=="4"),
                 #tod.2=as.numeric(dat$tod=="2"),tod.3=as.numeric(dat$tod=="3"),tod.4=as.numeric(dat$tod=="4"),
                 wgts=9,
                 samp=dim(dat)[1])

jags.inits = function(){list(bet = rnorm(28,0,.15),alph=rnorm(1,0,.15))}
jags.parms = c('w','bet','alph')

jinits=jags.inits()
jmod = jags.model(file=modelFilename, data=jags.data, inits = jags.inits(),n.chains=3, n.adapt=100)
#jmod = jags.model(file=modelFilename, data=jags.data,n.chains=3, n.adapt=100)   #inits = jags.inits(),
update(jmod, n.iter=100, by=10, progress.bar='text')
post = coda.samples(jmod, jags.parms, n.iter=5000, thin=10)
#dicsam=dic.samples(jmod, 1000, "popt")
mypost = as.matrix(post, chain=F)
plot(post)
summary(post)




```

```{r PSCL}
# zipform=formula(fishseen~ y + wc + cd + cm + sc + sr + ss + bd + bt + bh + d + t + lat + temp + tod +offset(frames))
# zipmod=zeroinfl(zipform,  dist = "poisson", link = "logit",data=dat);summary(zipmod)
# 
# ###Remove biotic variables
# zipform=formula(fishseen~ y + wc + cd + cm + sc + sr + ss +  bt + bh + d + t + lat + temp + tod +offset(frames))
# zipmod=zeroinfl(zipform,  dist = "poisson", link = "logit",data=dat);summary(zipmod)
# 
# zipform=formula(fishseen~ y + wc + cd + cm + sc + sr + ss +  bh + d + t + lat + temp + tod +offset(frames))
# zipmod=zeroinfl(zipform,  dist = "poisson", link = "logit",data=dat);summary(zipmod)
# 
# zipform=formula(fishseen~ y + wc + cd + cm + sc + sr + ss +  d + t + lat + temp + tod +offset(frames))
# zipmod=zeroinfl(zipform,  dist = "poisson", link = "logit",data=dat);summary(zipmod)
# 
# 
# 
# #### Remove Sebstrate type 
# zipform=formula(fishseen~ y + wc + cd + cm + sr + ss + bd + bt + bh + d + t + lat + temp + tod +offset(frames))
# zipmod=zeroinfl(zipform,  dist = "poisson", link = "logit",data=dat);summary(zipmod)
# 
# zipform=formula(fishseen~ y + wc + cd + cm + ss + bd + bt + bh + d + t + lat + temp + tod +offset(frames))
# zipmod=zeroinfl(zipform,  dist = "poisson", link = "logit",data=dat);summary(zipmod)
# 
# zipform=formula(fishseen~ y + wc + cd + cm + bd + bt + bh + d + t + lat + temp + tod +offset(frames))
# zipmod=zeroinfl(zipform,  dist = "poisson", link = "logit",data=dat);summary(zipmod)
# 
# 
# zipform=formula(fishseen~ y + wc + cd + cm + sc + ss + bd + bt + bh + d + t + lat + temp + tod +offset(frames))
# zipmod=zeroinfl(zipform,  dist = "poisson", link = "logit",data=dat);summary(zipmod)
# 
# zipform=formula(fishseen~ y + wc + cd + cm + sc + bd + bt + bh + d + t + lat + temp + tod +offset(frames))
# zipmod=zeroinfl(zipform,  dist = "poisson", link = "logit",data=dat);summary(zipmod)
# 
# 
# zipform=formula(fishseen~ y + wc + cd + cm + sc + sr + bd + bt + bh + d + t + lat + temp + tod +offset(frames))
# zipmod=zeroinfl(zipform,  dist = "poisson", link = "logit",data=dat);summary(zipmod)
# 
# zipform=formula(fishseen~ y + wc + cd + cm + sr  + bd + bt + bh + d + t + lat + temp + tod +offset(frames))
# zipmod=zeroinfl(zipform,  dist = "poisson", link = "logit",data=dat);summary(zipmod)
# 
# summary(zipmod)
# 
# #glm.step <- stepAIC(zipmod,direction="backward")
# 
# 
# windows(width=8,height=6,record=T)
# resids=residuals(zipmod)
# cbind(fitted(zipmod),dat$fishseen,fitted(zipmod)-dat$fishseen,resids)
# plot(fitted(zipmod),resids)
# qr.zipmod=qres.pois(zipmod)
# qqnorm(qr.zipmod,ylim=c(-4,10),main='QQplot residuals (qr.zipmod)',  cex=0.5)
# qqline(qr.zipmod)
# #qqnorm(resids,ylim=c(-4,10),main='QQplot residuals ',  cex=0.5)
# #qqline(resids)
# plot(dat$y,resids,xlab="Year",main="Residuals (zipmod)")
# plot(dat$wc,resids,xlab="Water Clarity",main="Residuals (zipmod)")
# plot(dat$cd,resids,xlab="Current Direction",main="Residuals (zipmod)")
# plot(dat$bd,resids,xlab="Biotic Diversity",main="Residuals (zipmod)")
# plot(dat$bt,resids,xlab="Biotic Type",main="Residuals (zipmod)")
# plot(dat$bh,resids,xlab="Biotic Height",main="Residuals (zipmod)")
# plot(dat$lat,resids,xlab="Latitude",main="Residuals (zipmod)")
# 
# hist(dat$fishseen,breaks=0:max(dat$fishseen),freq=T,right=TRUE,xlab='Aggregate Fish Counted', main='ZIP')  
# d=hist(predict(zipmod),breaks=0:max(dat$fishseen),plot=FALSE)
# lines(seq(0.5,max(dat$fishseen),by=1),d$counts, col="blue",type='l')      
# hist(dat$fishseen,breaks=0:max(dat$fishseen),freq=T,right=TRUE,xlab='Aggregate Fish Counted', main='ZIP',ylim=c(0,50))  
# lines(seq(0.5,max(dat$fishseen),by=1),d$counts, col="blue",type='b')      


# new.dat=expand.grid(y=levels(dat$y),
#                     wc=levels(dat$wc),
#                     cm=levels(dat$cm),
#                     cd=levels(dat$cd),
#                     #sc=levels(dat$sc),
#                     #bd=levels(dat$bd),
#                     bt=levels(dat$bt),
#                     #bh=levels(dat$bh),
#                     d=levels(dat$d),
#                     t=levels(dat$t),
#                     lat=levels(dat$lat),
#                     temp=levels(dat$temp),
#                     tod=levels(dat$tod),
#                     frames=1)
# 
# new.dat=cbind(new.dat,predict(zipmod,new.dat))
# names(new.dat)[dim(new.dat)[2]]="Predicted"
# resvec=summaryBy(Predicted~y,data=new.dat,FUN=mean)[,2]
# index = resvec/mean(resvec)
# plot(index,type='b')


#Now plot the simplified model
# zipmod=glm.step
# 
# resids=residuals(zipmod)
# plot(fitted(zipmod),resids)
# qr.zipmod=qres.pois(zipmod)
# qqnorm(qr.zipmod,ylim=c(-4,10),main='QQplot residuals (qr.zipmod)',  cex=0.5)
# qqline(qr.zipmod)
# plot(dat$y,resids,xlab="Year",main="Residuals (zipmod)")
# plot(dat$wc,resids,xlab="Water Clarity",main="Residuals (zipmod)")
# plot(dat$cd,resids,xlab="Current Direction",main="Residuals (zipmod)")
# plot(dat$bd,resids,xlab="Biotic Diversity",main="Residuals (zipmod)")
# plot(dat$bt,resids,xlab="Biotic Type",main="Residuals (zipmod)")
# plot(dat$bh,resids,xlab="Biotic Height",main="Residuals (zipmod)")
# plot(dat$lat,resids,xlab="Latitude",main="Residuals (zipmod)")
# 
# hist(dat$fishseen,breaks=0:39,freq=T,right=TRUE,xlab='Aggregate Fish Counted', main='ZIP')  
# d=hist(predict(zipmod),breaks=0:39,plot=FALSE)
# lines(seq(0.5,38.5,by=1),d$counts, col="blue",type='l')      
# hist(dat$fishseen,breaks=0:39,freq=T,right=TRUE,xlab='Aggregate Fish Counted', main='ZIP',ylim=c(0,50))  
# lines(seq(0.5,38.5,by=1),d$counts, col="blue",type='b')      


# new.dat=expand.grid(y=levels(dat$y),
#                     wc=levels(dat$wc),
#                     cm=levels(dat$cm),
#                     #cd=levels(dat$cd),
#                     #sc=levels(dat$sc),
#                     #bd=levels(dat$bd),
#                     bt=levels(dat$bt),
#                     #bh=levels(dat$bh),
#                     d=levels(dat$d),
#                     t=levels(dat$t),
#                     lat=levels(dat$lat),
#                     temp=levels(dat$temp),
#                     tod=levels(dat$tod),
#                     frames=1)
# 
# new.dat=cbind(new.dat,predict(zipmod,new.dat))
# names(new.dat)[dim(new.dat)[2]]="Predicted"
# resvec=summaryBy(Predicted~y,data=new.dat,FUN=mean)[,2]
# index = resvec/mean(resvec)
# plot(index,type='b')


```

```{r glmmandm}
# library(glmmADMB)
# admbzip=glmmadmb(fishseen~ y + wc + cd + cm  + sr  +  bt + d + t + lat + temp + tod +offset(frames), 
#                                         data=dat, 
#                                         zeroInflation=TRUE, 
#                                         family="poisson");admbzip
# 
# resids=residuals(admbzip)
# preds=(fitted(admbzip))
# cbind((predict(admbzip)),dat$fishseen,exp(predict(admbzip))-dat$fishseen,resids)
# plot(fitted(admbzip),resids)
# qr.admbzip=qres.pois(admbzip)
# qqnorm(resids,ylim=c(-4,10),main='QQplot residuals (qr.admbzip)',  cex=0.5)
# qqline(resids)
# hist(dat$fishseen,breaks=0:max(dat$fishseen),freq=T,right=TRUE,xlab='Aggregate Fish Counted', main='ZIP')  
# d=hist(preds,breaks=0:max(dat$fishseen),plot=FALSE)
# lines(seq(0.5,max(dat$fishseen),by=1),d$counts, col="blue",type='l')      
# hist(dat$fishseen,breaks=0:max(dat$fishseen),freq=T,right=TRUE,xlab='Aggregate Fish Counted', main='ZIP',ylim=c(0,500))  
# lines(seq(0.5,max(dat$fishseen),by=1),d$counts, col="blue",type='b')      
# 
# library(coefplot2)
# coefplot2(admbzip)

```


#      log.ypred[i] <- bet[1]+
# w[1]*(bet[2]*y2011[i]+bet[3]*y2012[i])+
# w[2]*(bet[4]*wc.1[i]+bet[5]*wc.2[i])+
# w[3]*(bet[6]*cd.s[i]+bet[7]*cd.t[i]+bet[8]*cd.u[i])+
# w[4]*(bet[9]*cm.s[i]+bet[10]*cm.u[i])+
# w[5]*(bet[11]*sc.l[i]+bet[12]*sc.m[i]+bet[13]*sc.n[i]+bet[14]*sc.u[i])+
# w[6]*(bet[15]*sr.l[i]+bet[16]*sr.m[i]+bet[17]*sr.u[i])+
# w[7]*(bet[18]*ss.cont[i]+bet[19]*ss.na[i]+bet[20]*ss.u[i])+
# w[8]*(bet[21]*bd.l[i]+bet[22]*bd.m[i]+bet[23]*bd.n[i]+bet[24]*bd.u[i])+
# w[9]*(bet[25]*bt.na[i]+bet[26]*bt.o[i]+bet[27]*bt.u[i])+
# w[10]*(bet[28]*bh.l[i]+bet[29]*bh.na[i]+bet[30]*bh.u[i])+
# w[11]*(bet[31]*d.2[i]+bet[32]*d.3[i]+bet[33]*d.4[i])+
# w[12]*(bet[34]*t.2[i]+bet[35]*t.3[i]+bet[36]*t.4[i])+
# w[13]*(bet[37]*lat.2[i]+bet[38]*lat.3[i]+bet[39]*lat.4[i])+
# w[14]*(bet[40]*temp.2[i]+bet[41]*temp.3[i]+bet[42]*temp.4[i])+
# w[15]*(bet[43]*tod.2[i]+bet[44]*tod.3[i]+bet[45]*tod.4[i])
